\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage{xcolor}
\definecolor{darkblue}{HTML}{000040}
\usepackage{hyperref}
\hypersetup{
	colorlinks=true,
	linkcolor=blue,
	urlcolor=darkblue,
}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{tikz}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}



\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

%-------------------------
% Custom commands
\newcommand{\orignalResumeItem}[2]{
  \item\small{
    \textbf{#1}{ #2 \vspace{-2pt}}
  }
}

\newcommand{\resumeItem}[2]{
  \item\small{
    { #2 \vspace{-2pt}}
  }
}
\newcommand{\sresumeItem}[1]{
  \item\small{
    { #1 \vspace{-2pt}}
  }
}
\newcommand{\resumePara}[1]{
  \item\small{
    { #1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubheadingLong}[5]{
	\vspace{-1pt}\item
	\begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
		\textbf{#1} & #2 \\
		\textit{\small #3} & \textit{\small #4} \\
	\end{tabular*}\vspace{3pt}
    \textit{\footnotesize #5}\vspace{-5pt}
}

\newcommand{\shortResumeSubheading}[2]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
    \end{tabular*}
  \vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\orignalResumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\newcommand{\ExternalLink}{%
	\tikz[x=1.2ex, y=1.2ex, baseline=-0.05ex]{% 
		\begin{scope}[x=1ex, y=1ex]
			\clip (-0.1,-0.1) 
			--++ (-0, 1.2) 
			--++ (0.6, 0) 
			--++ (0, -0.6) 
			--++ (0.6, 0) 
			--++ (0, -1);
			\path[draw, 
			line width = 0.5, 
			rounded corners=0.5] 
			(0,0) rectangle (1,1);
		\end{scope}
		\path[draw, line width = 0.5] (0.5, 0.5) 
		-- (1, 1);
		\path[draw, line width = 0.5] (0.6, 1) 
		-- (1, 1) -- (1, 0.6);
	}
}
%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{\href{http://pranavg.me/}{\Large Pranav Gade}} & Email: \href{mailto:pranavgade20@gmail.com}{pranavgade20@gmail.com}\\
  \href{http://pranavg.me/}{pranavg.me} & LinkedIn: \href{http://www.linkedin.com/in/pranav-gade/}{linkedin.com/in/pranav-gade} \\
\end{tabular*}

%-----------EDUCATION-----------------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheadingLong
      {Indian Institute of Information Technology}{Lucknow, India}
      {Bachelor of Technology in Computer Science and Artificial Intelligence; Current GPA: 9.53/10}{Dec. 2020 - present}
      {Relevant Coursework: Data Structures, Algorithms, Object Oriented Programming, Digital Communications, Automata Theory, Database Management Systems, Operating Systems, Artificial Intelligence, Big Data Analytics}
  \resumeSubHeadingListEnd


\section{Experience}
  \resumeSubHeadingListStart
    \resumeSubheading
      {QuantCo}{Z\"{u}rich, Switzerland}
      {SWE Intern}{Jun 2021 - Aug 2021}
      \resumeItemListStart
        \sresumeItem{Worked on QuantCo's internal toolchain for evaluating SQL databases performance for data science.}
        \sresumeItem{Containerized the benchmarker and deployed it to Google Kubernetes Engine.}
        \sresumeItem{Benchmarked and evaluated BigQuery, Microsoft SQL server, PostgreSQL, and Snowflake database systems.}
        \sresumeItem{Designed and developed QuantCo's engineering hiring challenge, \href{https://challenge.quantco.com}{challenge.quantco.com}}
      \resumeItemListEnd
    \resumeSubheading
      {KDE Community}{}
      {Open Source Developer, GSoC Mentor}{Nov 2018 - present}
      \resumeItemListStart
        \orignalResumeItem{networkmanager-qt:}{a Qt wrapper for NetworkManager API - during Google Code-in 2018}
        \orignalResumeItem{marK:}{a multimedia annotation tool for ML - during Season of KDE 2021 as a participant; and during Google Summer of Code 2021 as mentor.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd


\section{Awards \& Achievements}
  \resumeSubHeadingListStart

    \shortResumeSubheading
      {Google Code-in 2018 Grand Prize Winner}{2018}
      \resumeItemListStart
        \sresumeItem
          {\href{http://g.co/gci/}{Google Code-in} is a contest by Google to encourage participation in open-source software. I completed 34 tasks in the contest and was selected as the Grand Prize winner by \href{https://kde.org/}{KDE Community}.}
        \sresumeItem
          {As a part of the prize, I was invited to Google's Headquarters in Mountain View, California.}
      \resumeItemListEnd

    \shortResumeSubheading
      {Ranked 52 out of 15817 globally in PicoCTF}{2019}
      \resumeItemListStart
        \sresumeItem
          {CTFs are cybersecurity competitions consisting of a series of challenges where participants must reverse engineer, break, hack, or decrypt to solve the challenges. PicoCTF is a contest organized by security experts at Carnegie Mellon University.}
        \sresumeItem
          {My team was ranked 52nd out of 15817 among high school and college students from around the world.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd

%-----------PROJECTS-----------------
\section{Projects}
  \resumeSubHeadingListStart
    \resumeSubItem{\href{https://github.com/pranavgade20/jLHS}{jLHS}:}
      {\vspace{-2pt} fast and tiny HTTP/1.1 server written in Java without any dependencies, supports GET and POST requests}
    \resumeSubItem{\href{https://github.com/pranavgade20/ClassReader}{Java-Disassembler}:}
      {\vspace{-2pt} .class file parser and serializer. Also disassembles code from compiled Java code.}
    \resumeSubItem{\href{https://github.com/pranavgade20/FabricHax}{FabricHax}:}
	  {\vspace{-2pt}  A minecraft mod to automate repetitive tasks}
    \resumeSubItem{PhonePut:}
      {\vspace{-2pt} An android application that turns your device into an input device for your computer}
    \resumeSubItem{\href{https://github.com/pranavgade20/htcpcp-impl}{htcpcp-impl}:}
      {\vspace{-2pt} Implementation of rfc2324 - Hyper Text Coffee Pot Control Protocol (HTCPCP/1.0)}
    \resumeSubItem{\href{https://phabricator.kde.org/source/networkmanager-qt/}{networkmanager-qt}:}
      {\vspace{-2pt} NetworkManagerQt provides access to all NetworkManager features exposed to DBus API}
   \resumeSubItem{\href{https://invent.kde.org/education/mark}{marK}:}
      {\vspace{-2pt} A machine learning dataset annotation tool which allows users to annotate multiple types of data}
    \resumeSubItem{My website:}
      {\vspace{-2pt} \href{http://pranavgade20.github.io/}{pranavgade20.github.io}}
  \resumeSubHeadingListEnd


% --------PROGRAMMING SKILLS------------
\section{Skills}
 \resumeSubHeadingListStart
   \item{
     \textbf{Programming Languages/Frameworks}{: Java, Python, C++, C, JavaScript/NodeJS, Bash Scripting, Rust, R, Haskell, 8085 Assembly, x86 Assembly, Kotlin, Groovy}
   }
    \item{
      \vspace{-8pt}
      \textbf{Reverse Engineering/Information Security}{: Ghidra, Radare2, Android Studio, GDB, Wireshark}
    }
    \item{
      \vspace{-8pt}
      \textbf{Other Software}{: Linux, Docker, Kubernetes, Google Cloud, git/mercurial, Gradle, Android, PostgreSQL, Snowflake, MongoDB, Regex, JSON, LaTeX}
    }

 \resumeSubHeadingListEnd

\end{document}
